Methods

### 2024-03-12 methods.qmd
Added cluster charts to targets pipeline
Adding more metrics to the data collection
Initialising gh-pages branch

### Attempt 1

@@

>>>>

### Notes

@@

## Smoking PCAS

Metric 12 - Exception reporting for Smoking cessation support offered

<https://digital.nhs.uk/data-and-information/publications/statistical/quality-and-outcomes-framework-achievement-prevalence-and-exceptions-data/2022-23>

Donwloaded:

qof-2223-prev-ach-pca-ls-prac.xlsx

## References

<https://journals.sagepub.com/doi/epdf/10.1093/phr/117.3.273>
